Panel Seminars

### 2023-10-12 index.Rmd
Push front page w citation instructions

>>>>

# How to Cite{#how_to_cite}

If referencing marineomics.io, please use the following citation:

Bogan, S. N., Johns, J., Griffiths, J. S., Davenport, D., Smith, S. J., Schaal, S. M., Downey-Wall, A., Lou, R. N., Lotterhos, K., Guidry, M. E., Rivera, H. E., McGirr, J. A., Puritz, J. B., Roberts, S. B., and Silliman, K. (2023). A dynamic web resource for robust and reproducible genomics in nonmodel species: marineomics.io. Methods in Ecology and Evolution, 00, 1–8. https://doi.org/10.1111/2041-210X.14219
<br>

If referencing a specific page on marineomics.io please reference the above citation in addition to a reference to the individual page as follows:
<br>
LastName1, Initials1, LastName2, Initials2, etc. (Publication year) Webpage title. URL.

For the page "Choosing a Population Genomics Approach" the citation would be written as

Silliman, K. and Lou, R. N. (2022). Choosing a Population Genomics Approach. MarineOmics. https://marineomics.github.io/POP_01_choosing_population_genetics.html
